Social Conditions of Fear

### 2023-11-22 scripts/manuscript.qmd
cleaning

```{r}
#| label: coding all missing data as NA 
# NOT WORKING - Need to troubleshoot
missing_vec <- c(".i:  Inapplicable" , ".n: No answer", ".d: Do not Know/Cannot Choose", ".s: Skipped on Web")

no_na_data <- data %>% 
  mutate(across(c(id, age, sex, sexnow1, sexornt, degree, attend, raclive, happy, health, helpful, fair, trust, fear, partnrs5, racerank1, uscitzn, dwelown), ~ifelse(. %in% missing_vec, NA_character_, .)))

>>>>

```{r}
#| label: coding all missing data as NA 
# NOT WORKING - Need to troubleshoot
missing_vec <- c(".i:  Inapplicable", ".n: No answer", ".d: Do not Know/Cannot Choose", ".s: Skipped on Web")

na_data <- data %>% 
  mutate(across(c(id, age, sex, sexnow1, sexornt, degree, attend, raclive, happy, health, helpful, fair, trust, fear, partnrs5, racerank1, uscitzn, dwelown), ~ifelse(. %in% missing_vec, NA_character_, .)))
